Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-17 paper-ieee-trans.tex
Rephrase last paragraph of the abstract

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by a various number of European Commission funded software development
and e-Infrastructures creation, operation and management dedicated projects.
% the creation of software development and e-Infrastructure coordination dedicated projects. 
This work examines the evolution of the software engineering methodologies used in past and present
European Commission-funded projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the
foundation of the first project in 2001. In particular, we describe the team
organizational structure, %(what does it mean?)
 techniques and procedures that have guided the Quality
Assurance definitions in order to deliver quality software. We highlight the challenges
and barriers that have been faced throughout these years and how they were overcomed totally or
partially. To conclude, we discuss possible future directions in software
Quality Assurance methodologies for the upcoming projects.
\end{abstract}

>>>>

\begin{abstract}
From the advent of Grid technology as the new paradigm of distributed
computing to the current days of Cloud computing models, the continuous need
of new tools and services to match the scientific community requirements has been
addressed in Europe by a various number of projects dedicated to software development
and e-Infrastructure creation, operation and management.
% the creation of software development and e-Infrastructure coordination dedicated projects. 
This work examines the evolution of the software engineering methodologies used in past and
present European Commission-funded projects to illustrate how the research on software
reliability has progressed in Europe over the last 15 years following the foundation of the
first project in 2001. In particular, we will summarize the techniques and procedures
applied to deliver quality software, hightlighting the main challenges and barriers confronted
at the time, and how they were totally or partially overcomed. The base of knowledge collected
throughout these years, sustained by the advances in the area of software engineering,
definitely conformed a significant breakthrough in the reliability of software delivered in the
European research arena. Latest software development projects founded by the European 
Commission are good evidences of such insights, where the enforcement of Quality Assurance
procedures is present since the very early stages of the software development process.
\end{abstract}
